---
title: "MTCars data correlation between MPG and other variables"
author: "Gavin Kim"
date: "2017-1-12"
output: ioslides_presentation
---
```{r}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Executive Summary

This application is based on Regression Model lecture's final assessment of coursera data scientist course. I just re-worked my Rmd report to interactive shiny web application.

This report explores correlation between a set of variables and miles per gallon(MPG) from “Mortor Trend”magazine(1973). The question what this report do answer is below.

 - Is an automatic or manual transmission better for MPG
 - Quantify the MPG difference between automatic and manual transmissions

## EDA

You can get the information of correlation between MPG and another variable on "EDA" tab.

```{r fig.width=6, fig.height=4, echo=FALSE}
library(png)
library(grid)
img <- readPNG("Figure/EDASample1.png")
grid.raster(img)
```

## Build a Linear Regression Model

Also, You can build a your own model on "Regression Analysis" tab.

```{r fig.width=6, fig.height=4, echo=FALSE}
library(png)
library(grid)
img <- readPNG("Figure/BuildSample1.png")
grid.raster(img)
```

## URLs

This is URL of my app, github and github-page.

Shiny app: 
https://floodzero.shinyapps.io/FinalShinyApp/

github: 
https://github.com/floodZero/DevDataProductFinalAssignment

github-page: 
https://floodZero.github.io/DevDataProductFinalAssignment/FinalShinyApp.html
